% LaTeX Resume for KAVIN NARESH G R
\documentclass[letterpaper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{longtable}  % Added longtable package

\begin{document}

\pagestyle{empty} % No page numbers

\begin{center}
\textbf{\LARGE KAVIN NARESH G R} \\
\textit{kavinnareshgr@gmail.com \quad +91 9751983211} \\
\href{https://www.linkedin.com/in/kavin-naresh-g-r/}{LinkedIn} \quad \href{https://github.com/kavin-naresh}{GitHub} \quad \href{https://leetcode.com/kavinnareshgr/}{LeetCode} \quad \href{https://www.codechef.com/users/kavinnaresh/}{CodeChef} \quad \href{https://auth.geeksforgeeks.org/user/kavinnan6sj}{GeeksforGeeks}
\end{center}

\section*{Qualification}
\begin{tabular}{l l l l}
\textbf{Degree} & \textbf{Institution} & \textbf{CGPA/Percentage} & \textbf{Year of Passing} \\
B.E.(CSE) & Ramco Institute of Technology, Rajapalayam & 8.0 & 2021 \\
\end{tabular}

\section*{Project Experience}

\subsection*{Infosys: ESB Mule Modernization (Feb 2021 -- Sep 2023)}
To manage business operations with fewer downtime risks, new reusable Gradle-based spring boot microservices have been created to handle MuleSoft ETL Api transformation and upgrade business area application services that depend on consumer usage. These microservices are deployed in on-premises Kubernetes. Such an action will simplify our processes and open the door for any future improvements to Mule's services that involve ETL processes of any sort.

\textbf{Responsibilities:}
\begin{itemize}[left=0pt, label={}]
    \item Deploying migrated services for performance and load testing.
    \item Documenting and comparing outcomes before and after.
    \item Monitoring using ELK and Dynatrace after deployment in prod.
    \item Incident Response: Identifying root causes and implementing solutions.
    \item Version Control: Using Git for code checkout and merging.
    \item Configuring Kubernetes pipeline and deploying using CICD pipeline.
    \item Warranty support after application deployment.
\end{itemize}

\subsection*{Previous Company: Chainsys (Oracle Fusion Consultant)}
Worked as an Oracle Fusion Consultant, specializing in BI reports and Oracle EBS apps.

\subsection*{College Academic Projects}

\textbf{E-commerce Website | Java, Spring Boot, MySQL, and Angular}
\begin{itemize}[left=0pt, label={}]
    \item Developed an E-commerce website with Angular frontend and Spring Boot backend.
    \item Used Hibernate JPA for ORM mapping and Okta OAuth2 for user registration and authentication.
\end{itemize}

\section*{Achievements and Certifications}

\begin{itemize}[left=0pt, label={}]
    \item Step into Robotic Process Automation and Game Development Using Pygame at GUVI.
    \item NEW INDIA LEARNATHON 2020 organized by ICT Academy.
    \item Getting Started with AI on Jetson with Deep Stream for Video Analytics at NVIDIA.
    \item Robotic Process Automation at Automation Anywhere Enterprises.
    \item Cybersecurity Essential at CISCO Networking Academy.
    \item Career Edge - Knockdown the Lockdown at TCSION.
    \item Machine Learning \& Deep Learning Onramp at Math Work.
    \item Introduction to IoT at CISCO Networking Academy.
    \item Google Ads Search Certification, Google Cloud Platform Business Professional Accreditation, The Fundamentals of Digital Marketing at Google.
    \item Stepathon course by The Hindu (Scored 8.4/10).
    \item Certifications in Deep Learning, Full-Stack Web Development with React, and Big Data from Coursera.
\end{itemize}

\section*{Skills}

\textbf{Programming:} Java (DSA, IBM MQ, Spring Boot), Python (Selenium, Numpy, Pandas, Matplotlib), SQL \& PLSQL, TypeScript (Angular 9 framework).

\textbf{Skillset:} Core Java, Web development and testing, API Rest web services, Node.js.

\textbf{Development Tools:} Android Studio, Visual Studio, Spring Boot IDE.

\textbf{Operating System:} Windows 7/10, Linux.

\textbf{DevOps:} GitLab, Maven, Gradle, Jenkins, SonarQube, IBM Urban Code, Ansible Tower, Docker, Jira, Slack integrations, Dynatrace dashboard, ELK monitoring, Load runner.

\textbf{Domain Network:} Active Directory, SharePoint.

\textbf{Databases:} Oracle, MySQL, SQL Server. NoSQL: MongoDB \& Postgres.

\textbf{Servers:} WebSphere 7 \& 9, Tomcat.

\textbf{Design Tools:} ArgoUML, Lucid charts.

\textbf{SDLC Methodologies:} Waterfall \& Agile.





\section*{Languages}

\begin{itemize}
    \item English
    \item Tamil
    \item Telugu
\end{itemize}

\end{document}
