% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\begin{quote}
Vishal Kumar\\
Bangalore, Karnataka
\end{quote}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
+91 8789937028
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
vishal80020@gmail.com
\end{quote}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
https://www.linkedin.com/in/vishal56789/
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

\begin{quote}
\textbf{Education}
\end{quote}



\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()


\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{School of Engineering, CUSAT}\\
\emph{Bachelor of Technology in Computer Science and Engineering(CGPA of
8.94)}
\end{quote}\strut
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{July 2016 - Aug 2020} \emph{Kochi, Kerala, India}
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\bottomrule()


\end{longtable}

\begin{quote}
\textbf{Experience}
\end{quote}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Publicis Sapient}\\
\emph{Associate Technology L1}
\end{quote}\strut
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{May 2021 -- May 2023}\\
\emph{Bengaluru, India}
\end{quote}\strut
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

\begin{quote}
\emph{•} Worked as Spring boot backend developer at Publicis Sapient.
Responsible for creating REST APIs with JPA Hibernate and MYSQL\\
\emph{•} Worked on the scheduler and cron jobs to fetch the job details
from a third party. Integrated Solr Search with Spring boot application
and indexed the API responses after transformation as the document in
Solr.

\emph{•} Worked on AWS Cognito to integrate the user login and used AWS
SDK to interact with various services provided by AWS like S3 bucket,
EC2, Dynamo DB.

\textbf{C3M Cloud Control} \textbf{Feb 2021 -- Apr2021}

\emph{Software Engineer} \emph{Bengaluru, India} \emph{•} Worked on REST
APIs using Spring boot which can be consumed by the client to get all
the policy details attached to AWS services with an alert message which
indicates that a particular service does not have an appropriate policy
attached as per standards. AWS Java SDK was used to fetch policy
details.

\textbf{Projects}

\textbf{Image Translator} \emph{\textbar{} Python3, Angular, Google
Cloud Vision, and Translation API, Anaconda Jupyter NoteBook} \emph{•} A
Web app that recognizes the object when you place it in front of your
webcam and speaks up its detected label into seven different languages.
A convolutional neural network was trained on the CIFAR100 dataset for
image recognition with an accuracy of 86.36 and used google cloud
translation/speech API for label translation and speech.

\textbf{E-commerce Website} \emph{\textbar{} Java, Spring Boot, MySQL
and Angular}\\
\emph{•} Developed an E-commerce website using angular as FrontEnd and
spring boot as a backend to create REST APIs and MySQL to store the
product, user, and order details\\
\emph{•} Used Hibernate JPA implementation for ORM mapping and to
support CRUD operation to database.

\emph{•} Used Okta Oauth2 third-party libraries to handle users'
registration and authentication.

\textbf{Achievements and Certifications}

\emph{•} Highest rating of \textbf{1684} and rated as \textbf{3*} at
Codechef, which is one of the top sites in terms of participation of
programmers across the globe.

\emph{•} Secured in Codechef's Long Challenge in June 2022 among 18550
participants.

\emph{•} Learnt key Spring Boot 3 features: Core, Annotations, Java
Config, Spring MVC, Hibernate/JPA, and Maven\\
\emph{•} The Course was all about the basics of Android development and
as part of this course weather app was built.

\emph{•} Learnt the basic classifications and clustering algorithms used
in machine learning.

\textbf{Profile Links}

\emph{•}\\
\emph{•}\\
\emph{•}\\
\emph{•}

\textbf{Technical Skills}

\textbf{Languages}: C++, Java, Python, MySQL\\
\textbf{Technologies/Frameworks/Libraries}: Spring, Spring boot, Angular

\textbf{Languages}

\emph{•} Hindi\\
\emph{•} English
\end{quote}

\end{document}
