%-------------------------
% Resume in Latex
% Author: Kavin Naresh
% License: MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.3in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.1in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-15pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-11pt}]


%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeEducationHeading}[6]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-15pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Kavin Naresh G R} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:905314204536}{+91 9751983211}
    $|$
    \faAt \hspace{.5pt} \href{mailto:kavinnares@gmail.com}{kavinnares@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/kavin-naresh-g-r/}{LinkedIn}
    $|$
    \faGlobe \hspace{.5pt} \href{https://kavinkavin16.github.io/portfolio/}{Portfolio}
     $|$
    \faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/e3e6FQX7A46s8PVY6}{Bengaluru, Karnataka}
\end{center}

%----------- EDUCATION -----------

\section{Education}
\vspace{6pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
{\textbf{\href{https://www.ritrjpm.ac.in/}{Ramco Institute of Technology}}} % Link added to the text
%      {Ramco Institute of Technology}
      {{\href{https://maps.app.goo.gl/hTBB5A97REHcSghFA}{Virudhunagar, TamilNadu}}}
      {B.E. in Computer Science \& Engineering;   \textbf{(CGPA of 8.0)}}{March 2017 \textbf{--}May 2021}
      {\textbf{}}{ \textbf{}}
  \resumeSubHeadingListEnd



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{6pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{\href{https://www.infosys.com/}{Infosys Limited}}}{{\href{https://maps.app.goo.gl/e3e6FQX7A46s8PVY6}{Bengaluru, Karnataka}}}
      {Systems Engineer}{Nov 2021 \textbf{--} Present, Full-time}
        \resumeItemListStart
           \resumeItem{Worked on deploying Gradle-based Spring Boot microservices for MuleSoft ETL API transformations, ensuring seamless business operations.}
           \resumeItem{Worked on the scheduler and cron jobs to fetch the job details from a third party. Integrated Solr Search with Spring
boot application and indexed the API responses after transformation as the document in Solr.}
           \resumeItem{Worked on AWS Cognito to integrate the user login and used AWS SDK to interact with various services provided by
AWS like S3 bucket, EC2, Dynamo DB.}
        \resumeItemListEnd

    \resumeSubheading
      {\textbf{\href{https://www.chainsys.com/}{Chain-Sys India Pvt Ltd}}}{{\href{https://maps.app.goo.gl/CkDDxi68E4NwArMKA}{Chennai, TamilNadu}}}
      {Oracle Fusion Consultant}{Mar 2021 \textbf{--} Sep 2021, Full-time}
        \resumeItemListStart
            \resumeItem{Worked as an Oracle Fusion Consultant, I excelled in BI, OTBI report development, Oracle E-Business Suite optimization, data analysis, and dashboard creation within Oracle Fusion instances.}
            \resumeItem{Leveraging SQL and PL/SQL, I crafted comprehensive reports, optimized EBS applications, and implemented insightful dashboards, contributing to efficient and data-driven business processes.}
            \resumeItem{Worked as OIC consultant for top-tier singapore clients.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%----------- RESEARCH EXPERIENCE -----------

\section{Projects}
  \vspace{6pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Driver Drowsiness Detection}{\textbf{}Virudhunagar, TamilNadu}
      {Python3, Angular, Anaconda Jupyter}{Nov 2020 \textbf{--} Feb 2021, Final year project}
        \resumeItemListStart
            \resumeItem{The developed app employs a CNN model for Driver Drowsiness Detection, utilizing OpenCV for face and eye tracking. The system continuously monitors the user's eye state, triggering an alarm for drowsiness. The absence of an included Angular UI implies a separate development for user control and monitoring features.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Mess Management System}{Virudhunagar, TamilNadu}
      {Java, Spring Boot, MySQL and Angular}{Oct 2019 \textbf{--} Feb 2020, Third year project}
        \resumeItemListStart
            \resumeItem{Developed an in-house Mess web  project using angular as FrontEnd and spring boot as a backend to create REST APIs and MySQL to store the product, user, and order details.}
            \resumeItem{Used Hibernate JPA implementation for ORM mapping and to support CRUD operation to database.}
            \resumeItem{ Used Okta Oauth2 third-party libraries to handle user's registration and authentication.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

 \section{Awards \& Achievements}
 \vspace{4pt}
 \resumeSubHeadingListStart
 \small{\item{

\textbf{\href{https://www.linkedin.com/posts/shakthivarman-thangavelu_happy-to-announce-that-i-have-lead-this-young-activity-7132986612459655168-5suN?utm_source=share&utm_medium=member_desktop}{IBM WatsonX Challenge for GSI:}} Leveraged Watson Discovery model for precise and efficient answers in developing an intelligent banking bot during a hackathon. (Nov 2023)

 \textbf{RPA:}{ Step into Robotic Process Automation and Game Development Using Pygame at GUVI. (Jul 2022)} \\ \vspace{3pt}

\textbf{Math Work:}{ Machine Learning \& Deep Learning Onramp at Math Work. (Dec 2021 \textbf{--} Jun 2022)} \\ \vspace{3pt}
    
\textbf{Stepathon:}{ Stepathon course by The Hindu (Scored 8.4/10). (Jul 2018)} \\ \vspace{3pt}
        
\textbf{Coursera:}{ Deep Learning. (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}
        
 \textbf{IBM:}{Cybersecurity Roles, Processes \& Operating System Security. (July  2020)} \\ \vspace{3pt}
       
 }}
\resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Programming Languages:}{ Java, Python, JavaScript, TypeScript, SQL \& PLSQL} \\ \vspace{3pt}
        
        \textbf{Technologies/Frameworks/Libraries:}{ Springboot, Web Services (REST \& SOAP), Kubernetes, IBM MQ, Linux, Angular, MongoDB, AWS } \\ \vspace{3pt}

         \textbf{Linguistic communication:}{ English, Tamil, Kannada, Telugu} \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
