%-------------------------
% Resume in LaTeX
% Author: Kavin Naresh
% License: MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage{comment}
% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.3in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.2in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\color{blue}
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-15pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeOrganizationHeading}[3]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\definecolor{mygreen}{RGB}{69, 123, 138}

\definecolor{myblue}{RGB}{20, 27, 110}

\definecolor{myred}{RGB}{255, 0, 0}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Kavin Naresh G R} \\ \vspace{1pt}
    \small
    \textcolor{mygreen}{\faMobile \hspace{.5pt} \href{tel:9751983211}{+91 9751983211}}
    $|$
    \textcolor{myred}{\faAt \hspace{.5pt} \href{mailto:kavinnares@gmail.com}{kavinnares@gmail.com}}
    $|$
    \textcolor{RoyalBlue}{\faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/kavin-naresh-g-r/}{LinkedIn/kavin-naresh-g-r}}
    $|$
    \textcolor{myblue}{\faGlobe \hspace{.5pt} \href{https://kavinkavin16.github.io/portfolio/}{Portfolio}}
    $|$
    \textcolor{DarkOrchid}{\faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/7d4xVmMTN6pnK8Dj8}{Madurai, TamilNadu}}
\end{center}

%----------- CAREER OBJECTIVE -----------
\section{Career Objective}
  \vspace{6pt}
Passionate and skilled Full Stack Developer with over 3 years of experience in designing, implementing, and managing scalable front-end and back-end applications. Proficient in AWS cloud services and committed to driving innovation, enhancing technical expertise, and contributing to organizational growth through continuous learning and resilience.

%----------- WORK EXPERIENCE -----------

\section{Professional Summary}
  \vspace{6pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{\href{https://www.infosys.com/}{Infosys Limited}}}{{\href{https://maps.app.goo.gl/e3e6FQX7A46s8PVY6}{Bengaluru, Karnataka}}}
      {Systems Engineer}{Nov 2021 \textbf{--} Present, Full-time}
        \resumeItemListStart
	\resumeItem{Extensive experience in design, implementation, and support of projects using frontend and backend frameworks.}
	\resumeItem{Specialized in developing REST APIs using Java/Spring Boot.}
	\resumeItem{Proficient in developing web pages using HTML, CSS, TypeScript, and Angular.}
	\resumeItem{Skilled in containerization and orchestration technologies like Docker and Kubernetes.}
	\resumeItem{Experience with message brokers such as IBM MQ for asynchronous communication.}
	\resumeItem{Expertise in creating CI/CD pipelines using Jenkins and deploying applications on AWS Cloud.}
	\resumeItem{Proficient in using Spring JPA for data persistence and implementing circuit breaker patterns for resilient applications.}
	\resumeItem{Hands-on experience with JSON, Spring Expression Language, and dynamic configuration tools for flexible workflows.}
	\resumeItem{Experienced in identifying and fixing web-application security vulnerabilities using tools like SonarQube and Checkmarx.}
	\resumeItem{Strong knowledge of version control tools such as Git, GitHub, and SVN/Tortoise SVN.}
	\resumeItem{Proficient in writing Unit Tests using JUnit and conducting integration testing.}
	\resumeItem{Solid understanding of Agile SDLC methodologies, actively participating in sprints and collaborating across teams.}

        \resumeItemListEnd


  \resumeSubHeadingListEnd
%----------- PROJECT EXPERIENCE -----------
         \vspace{3pt}
       \section{My Major Assignments at Infosys Limited}
         \vspace{6pt}
         \resumeSubHeadingListStart
         
     \resumeSubheading
             {Northwestern Mutual}{Bangalore, Karnataka}
             {Java, Spring Boot, Next Js, Kubernetes, Docker, AWS and UAT}{Nov 2021 \textbf{--} Present}
               \resumeItemListStart
		\resumeItem{Implemented Gradle-based Spring Boot microservices for MuleSoft ETL API transformations, ensuring smooth business operations.}
		\resumeItem{Integrated Solr Search with the Spring Boot application to index API responses post-transformation.}
		\resumeItem{Utilized Docker containers for packaging and deploying applications, ensuring consistency across development and production environments.}
		\resumeItem{Deployed and managed microservices using Kubernetes, streamlining scalability and orchestration of containerized applications.}
		\resumeItem{Implemented XML data parsing using DOM and SAX parsers to process and transform data efficiently for integration workflows.}
		\resumeItem{Leveraged IBM MQ as an asynchronous message broker to enable reliable and decoupled communication between microservices.}
		\resumeItem{Conducted meticulous migration procedures and executed pre-deployment and performance testing using LoadRunner.}
		\resumeItem{Defined transformation conditions in a JSON file using Spring Expression Language.}
		\resumeItem{Collaborated in an Agile development environment, designing and implementing RESTful APIs using Java and Spring Boot, enabling seamless communication between client applications and server services.}
		\resumeItem{Developed over 50+ screens and new UI components in an Agile SDLC environment using Angular.}
		\resumeItem{Enhanced and modernized legacy web applications to Java-based platforms, ensuring compatibility across modules.}
		\resumeItem{Worked closely with QA teams to identify and resolve software defects, delivering high-quality solutions.}
               \resumeItemListEnd
           
         \resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Most Recent Awards \& Achievements}
\vspace{0.1pt}
\resumeSubHeadingListStart
\small{\item{
    \resumeSubheading
      {Math Expression OCR Detection}{Bengaluru, Karnataka}
      {Python3, Angular, Anaconda Jupyter}{Jan 2024 -- Apr 2024, Infosys Techzooka (Team: 4)}
        \resumeItemListStart
            \resumeItem{Developed an Angular-based frontend for uploading handwritten math expressions. Integrated a deep learning model using the Tesseract library in Python for OCR and bounding box detection, trained on inkml files for Greek, Indian math symbols, alphabets, and numbers. The system generates LaTeX code to produce PDFs from detected OCR of handwritten images uploaded through the Angular frontend.}
        \resumeItemListEnd

  \resumeSubheading
  {IBM WatsonX Challenge for GSI}
  {\textbf{Bengaluru, Karnataka}}
  {IBM - Watsonx Assistant, Watsonx.ai, and Watson Discovery}
  {Nov 2023 -- Dec 2023, Infosys Techzooka (Team: 4)}
  \resumeItemListStart
      \resumeItem{Won 1st prize in the IBM challenge by creating an intelligent banking virtual agent leveraging the Watson Discovery model for precise and efficient answers.}
      \resumeItem{My Contribution: Handled the prompt for user payments and account-related details and configured Watson Discovery in the Banking Bot.}
  \resumeItemListEnd
  \vspace{1pt} % Adjust spacing if needed
  \small{\textcolor{blue}{(LinkedIn: \href{https://www.linkedin.com/posts/shakthivarman-thangavelu_happy-to-announce-that-i-have-lead-this-young-activity-7132986612459655168-5suN?utm_source=share&utm_medium=member_desktop}{View Post})}}

}}
\resumeSubHeadingListEnd


%--------------- CAPSTONE PROJECTS-----------------
 \section{Capstone Projects}
 \vspace{6pt}
 \resumeSubHeadingListStart
 \small{\item{
\textbf{ E-Commerce Application} \vspace{-4pt}
 \resumeItemListStart
	            \resumeItem{Project Description: It is an order management application for user to buy different product and has features like wish list, add to cart, place order and reward points.}
       		 \resumeItem{My Contribution: I was involved in CRUD development activities with RESTful web services. Used Technologies: Java, Spring boot and Spring Microservices}
        \resumeItemListEnd
 \vspace{2pt}
\textbf{CI/CD implementation in AWS Cloud} \vspace{-4pt}

 \resumeItemListStart
	            \resumeItem{Project Description: Deploying the spring boot application in EC2 instance using CI/CD technologies.}
		 \resumeItem{AWS Services Used: Code commit, Code build, Code Deploy and Code Pipeline, EC2 instance, S3, RDS, IAM}
        \resumeItemListEnd

       
 }}
\resumeSubHeadingListEnd
%----------- INTERNSHIP EXPERIENCE -----------
 \begin{comment}
\section{Internship Experience}
  \vspace{6pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{\href{https://www.chainsys.com/}{Chain-Sys India Pvt Ltd}}}{{\href{https://maps.app.goo.gl/CkDDxi68E4NwArMKA}{Chennai, TamilNadu}}}
      {Oracle Fusion Consultant}{Mar 2021 \textbf{--} Sep 2021, Internship}
        \resumeItemListStart
            \resumeItem{Worked as an Oracle Fusion Consultant, I excelled in BI, OTBI report development, Oracle E-Business Suite optimization, data analysis, and dashboard creation within Oracle Fusion instances.}
            \resumeItem{Leveraging SQL and PL/SQL, I crafted comprehensive reports, optimized EBS applications, and implemented insightful dashboards, contributing to efficient and data-driven business processes.}
            \resumeItem{Worked as OIC consultant for top-tier singapore clients.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd
 \end{comment}
%----------- EDUCATION -----------

\section{Education}
\vspace{6pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
{\textbf{\href{https://www.ritrjpm.ac.in/}{Ramco Institute of Technology}}} % Link added to the text
%      {Ramco Institute of Technology}
      {{\href{https://maps.app.goo.gl/hTBB5A97REHcSghFA}{Virudhunagar, TamilNadu}}}
      {B.E. in Computer Science \& Engineering;   \textbf{(CGPA of 8.0)}}{March 2017 \textbf{--}May 2021}
      {\textbf{}}{ \textbf{}}
  \resumeSubHeadingListEnd
        \vspace{3pt}
%----------- RESEARCH EXPERIENCE -----------
 \begin{comment}
        \vspace{3pt}
       \section{Academic Projects}
         \vspace{6pt}
         \resumeSubHeadingListStart
         
           \resumeSubheading
             {Driver Drowsiness Detection}{\textbf{}Virudhunagar, TamilNadu}
             {Python3, Angular, Anaconda Jupyter}{Nov 2020 \textbf{--} Feb 2021, Final year project}
               \resumeItemListStart
                   \resumeItem{The developed app employs a CNN model for Driver Drowsiness Detection, utilizing OpenCV for face and eye tracking. The system continuously monitors the user's eye state, triggering an alarm for drowsiness. The absence of an     included Angular UI implies a separate development for user control and monitoring features.}
               \resumeItemListEnd
           
           \resumeSubheading
             {Mess Management System}{Virudhunagar, TamilNadu}
             {Java, Spring Boot, MySQL and Angular}{Oct 2019 \textbf{--} Feb 2020, Third year project}
               \resumeItemListStart
                   \resumeItem{Developed an in-house Mess web  project using angular as FrontEnd and spring boot as a backend to create REST APIs and MySQL to store the product, user, and order details.}
                   \resumeItem{Used Hibernate JPA implementation for ORM mapping and to support CRUD operation to database.}
                   \resumeItem{ Used Okta Oauth2 third-party libraries to handle user's registration and authentication.}
               \resumeItemListEnd
           
         \resumeSubHeadingListEnd



\end{comment}

%----------- SKILLS -----------
% \vspace{3pt}
\section{Skills}
  \vspace{6pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming Languages:}{ Java, Python, Js,Ts, SQL \& PLSQL} \\ \vspace{3pt}
        \textbf{Technologies/Frameworks/Libraries:}{ Springboot, Web Services (REST \& SOAP), Kubernetes, IBM MQ, Linux, Next Js, Angular, MongoDB, AWS } \\ \vspace{3pt}
        \textbf{Version Control, IDE and Iaas:}{ Git, Intellij and Terraform } \\ \vspace{3pt}
        \textbf{Security tools:}{ SonarQube, CheckMarx} \\ \vspace{3pt}
        \textbf{AWS Cloud Services:}{ SDK, EC2, RDS, Lamda, S3, CI/CD, IAM, SQS, SNS, ECS/ECR, CloudWatch and CloudTrail. } \\ \vspace{3pt}
        \textbf{AI:}{ Generative AI and GitHub Copilot} \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd
%-----------  CERTIFICATIONS  -----------
% \vspace{3pt}
\section{Certifications}
  \vspace{6pt}
  \resumeSubHeadingListStart         
   \small{\item{
                   {Infosys Certified Java SE8 Developer.} \\ \vspace{3pt}
                   {Infosys Certified Spring Microservice Developer.} \\ \vspace{3pt}
                   {Infosys Certified Spring Associate.} \\ \vspace{3pt}
                   {Infosys Certified Angular Associate.} \\ \vspace{3pt}
                   {Infosys Certified Frontend Web Developer.} \\ \vspace{3pt}
                   {Infosys Global Agile Developer Certification.} \\ \vspace{3pt}
    }}

  \resumeSubHeadingListEnd

%----------- Personal aspects -----------

\section{Personal Aspets}
  \vspace{6pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Father Name :}{ Rengaraj G} \\ \vspace{3pt}
        \textbf{Total Experience :}{ 3.5 years} \\ \vspace{3pt}
        \textbf{Marital Status :}{ Single} \\ \vspace{3pt}
        \textbf{Personal Traits :}{ Interested in learning new things, Smart working, Excellent leadership skills, Interested to Travel and Flexible.} \\ \vspace{3pt}
        \textbf{Linguistic communication :}{ English, Tamil, Kannada, Telugu} \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd


%----------- DECLARATION -----------

\section{Declaration}
  \vspace{6pt}
  
  {\textbf{I hereby declare that the details furnished above are true and correct to the best of my knowledge.}}
  
  \begin{flushleft}
    \textbf{Place: Madurai, TamilNadu}
  \end{flushleft}
  
  \begin{flushright}
    \textbf{-- Kavin Naresh G R}
  \end{flushright}


%-------------------------------------------
\end{document}
