%-------------------------
% Resume in LaTeX
% Author: Yogalakshmi Palanivel
% License: MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{multicol}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.3in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.2in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\color{blue}
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-15pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeOrganizationHeading}[3]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\definecolor{mygreen}{RGB}{69, 123, 138}

\definecolor{myblue}{RGB}{20, 27, 110}

\definecolor{myred}{RGB}{255, 0, 0}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Yogalakshmi Palanivel} \\ \vspace{1pt}
    \small
    \textcolor{mygreen}{\faMobile \hspace{.5pt} \href{tel:9566319580}{+91 9566319580}}
    $|$
    \textcolor{myred}{\faAt \hspace{.5pt} \href{mailto:yogalakshmi.pm176@gmail.com}{yogalakshmi.pm176@gmail.com}}
    $|$
    \textcolor{RoyalBlue}{\faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/yogalakshmi-palanivel-0318181a0}{LinkedIn/yogalakshmi-palanivel}}
%    $|$
%  \textcolor{myblue}{\faGlobe \hspace{.5pt} \href{https://kavinkavin16.github.io/portfolio/}{Portfolio}}
    $|$
    \textcolor{DarkOrchid}{\faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/tpdEWqiBxRWC1Pg87}{Electronic City, Bangalore}}
\end{center}

%----------- CAREER OBJECTIVE -----------
\section{Career Objective}
  \vspace{6pt}
Experienced Full Stack Developer with 3 years of experience in front-end and back-end development. Seeking
opportunities to enhance my skills and contribute to organizational growth by leveraging my technical expertise and
passion for innovation.

%----------- WORK EXPERIENCE -----------

\section{Professional Summary}
  \vspace{6pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{\href{https://www.infosys.com/}{Infosys Limited}}}{{\href{https://maps.app.goo.gl/e3e6FQX7A46s8PVY6}{Bengaluru, Karnataka}}}
      {Senior Systems Engineer}{Sept 2021 \textbf{--} Present, Full-time}
        \resumeItemListStart
           \resumeItem{Extensive experience in design, implementation, and support of projects using frontend and backend frameworks.}
           \resumeItem{Specialized in developing REST APIs using Java/Spring Boot.}
           \resumeItem{Developed web pages using HTML, CSS, TypeScript, and Angular.}
	 \resumeItem{Played a key role in writing Functional Specification Documents, Test Scenarios, and Unit Test Plans.}  
	\resumeItem{Led the development of over 50+ screens in an Agile SDLC environment, modifying and enhancing web applications from legacy systems to modern Java-based applications.}
	\resumeItem{Worked on creating REST APIs and developing new UI components using Angular.}
	\resumeItem{Managed code congurations using GitHub and SVN/Tortoise SVN tools.}
	\resumeItem{Built and deployed applications using Jenkins and AWS Cloud.}
	\resumeItem{Identied and xed web-application security vulnerabilities using SonarQube/CheckMarx.}

        \resumeItemListEnd


  \resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Most Recent Awards \& Achievements}
\vspace{0.1pt}
\resumeSubHeadingListStart
\small{\item{
    \resumeSubheading
      {Math Expression OCR Detection}{Bengaluru, Karnataka}
      {Python3, Angular, Anaconda Jupyter}{Jan 2024 -- Apr 2024, Infosys Techzooka (Team: 6)}
        \resumeItemListStart
            \resumeItem{Developed an Angular-based frontend for uploading handwritten math expressions. Integrated a deep learning model using the Tesseract library in Python for OCR and bounding box detection, trained on inkml files for Greek, Indian math symbols, alphabets, and numbers. The system generates LaTeX code to produce PDFs from detected OCR of handwritten images uploaded through the Angular frontend.}
        \resumeItemListEnd

  \resumeSubheading
  {IBM WatsonX Challenge for GSI}
  {\textbf{Bengaluru, Karnataka}}
  {IBM - Watsonx Assistant, Watsonx.ai, and Watson Discovery}
  {Nov 2023 -- Dec 2023, Infosys Techzooka (Team: 6)}
  \resumeItemListStart
      \resumeItem{Won 1st prize in the IBM challenge by creating an intelligent banking virtual agent leveraging the Watson Discovery model for precise and efficient answers.}
      \resumeItem{My Contribution: Handled the prompt for user payments and account-related details and configured Watson Discovery in the Banking Bot.}
  \resumeItemListEnd

%  \vspace{1pt} % Adjust spacing if needed
%  \small{\textcolor{blue}{(LinkedIn: \href{https://www.linkedin.com/posts/shakthivarman-thangavelu_happy-to-announce-that-i-have-lead-this-young-activity-7132986612459655168-5suN?utm_source=share&utm_medium=member_desktop}{View Post})}}

}}
\resumeSubHeadingListEnd


%--------------- CAPSTONE PROJECTS-----------------
 \section{Capstone Projects}
 \vspace{6pt}
 \resumeSubHeadingListStart
 \small{\item{
\textbf{ E-Commerce Application} \vspace{-4pt}
 \resumeItemListStart
	            \resumeItem{Project Description: It is an order management application for user to buy different product and has features like wish list, add to cart, place order and reward points.}
       		 \resumeItem{My Contribution: I was involved in CRUD development activities with RESTful web services. Used Technologies: Java, Spring boot and Spring Microservices}
        \resumeItemListEnd
 \vspace{2pt}
\textbf{CI/CD implementation in AWS Cloud} \vspace{-4pt}

 \resumeItemListStart
	            \resumeItem{Project Description: Deploying the spring boot application in EC2 instance using CI/CD technologies.}
		 \resumeItem{AWS Services Used: Code commit, Code build, Code Deploy and Code Pipeline, EC2 instance, S3, RDS, IAM}
        \resumeItemListEnd

       
 }}
\resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
\vspace{6pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
{\textbf{\href{https://www.annauniv.edu/}{Anna University}}} % Link added to the text
%      {Ramco Institute of Technology}
      {{\href{https://g.co/kgs/7cMhyiW}{Chennai, TamilNadu}}}
      {B.Tech Information Technology;   \textbf{(CGPA of 8.0)}}{March 2017 \textbf{--}May 2021}
      {\textbf{}}{ \textbf{}}
  \resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------
         \vspace{3pt}
       \section{Projects}
         \vspace{6pt}
         \resumeSubHeadingListStart
         
           \resumeSubheading
             {M-CART APPLICATION}{\textbf{}Bangalore, Karnataka}
             {Java 8, Spring boot and Angular}{Sept 2021 \textbf{--} Dec 2021}
               \resumeItemListStart
                   \resumeItem{Developed backend REST APIs using Java/Spring Boot.}
                   \resumeItem{Designed and implemented web pages with HTML, CSS, TypeScript, and Angular.}
                   \resumeItem{Created detailed Functional Specification Documents and Test Cases.}
               \resumeItemListEnd
           
           \resumeSubheading
             {Burlington Northern Santa Fe Railways}{Bangalore, Karnataka}
             {Java, Spring Boot, MySQL and Angular}{Jan 2022 \textbf{--} Dec 2023}
               \resumeItemListStart
                   \resumeItem{Developed and modernized over 50+ web application screens in 20+ sprints.}
                   \resumeItem{Analyzed systems flow, data usage, and work processes to identify problem areas and develop solutions.}
                   \resumeItem{Wrote 100+ unit test cases to verify the functionality of user interfaces, back-end processing, and database interactions.}
               \resumeItemListEnd
           
     \resumeSubheading
             {Northwestern Mutual}{Bangalore, Karnataka}
             {Java, Spring Boot, AWS and UAT}{Jan 2024 \textbf{--} Present}
               \resumeItemListStart
                   \resumeItem{Managed the build and deployment of applications using Jenkins and AWS Cloud.}
                   \resumeItem{Performed code configurations and resolved security vulnerabilities identified in testing phases.}
                   \resumeItem{Worked with clients to resolve UAT and integration testing issues.}
               \resumeItemListEnd
           
         \resumeSubHeadingListEnd




%----------- SKILLS -----------
% \vspace{3pt}
\section{Skills}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Programming Languages:}{ Java, HTML, CSS, Js,Ts, SQL \& PLSQL} \\ \vspace{3pt}
        \textbf{Technologies/Frameworks/Libraries:}{ Springboot, Web Services (REST \& SOAP), Kubernetes, IBM MQ, Linux, React, Angular, MongoDB, AWS } \\ \vspace{3pt}
        \textbf{Version Control, IDE and Iaas:}{ SVN/Tortoise SVN,  Git, Intellij and Terraform } \\ \vspace{3pt}
        \textbf{AWS Cloud Services:}{ EC2, RDS, Lamda, S3, CI/CD, IAM, SQS, SNS, ECS/ECR, CloudWatch and CloudTrail. } \\ \vspace{3pt}
        \textbf{Security tools:}{ SonarQube, CheckMarx} \\ \vspace{3pt}
        \textbf{AI:}{ Generative AI and GitHub Copilot} \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd

%-----------  CERTIFICATIONS  -----------
% \vspace{3pt}
\section{Certifications}
  \vspace{3pt}
  \resumeSubHeadingListStart         
    \resumeSubheading
             %{Northwestern Mutual}{Bangalore, Karnataka}
             %{Java, Spring Boot, AWS and UAT}{Jan 2024 \textbf{--} Present}
               \resumeItemListStart
                   \resumeItem{Infosys Certified Java SE8 Developer.}
                   \resumeItem{Infosys Certified Spring Microservice Developer.}
                   \resumeItem{Infosys Certified Spring Associate.}
                   \resumeItem{Infosys Certified Angular Associate.}
                   \resumeItem{Infosys Certified Frontend Web Developer.}
                   \resumeItem{Infosys Global Agile Developer Certification.}
               \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- Personal aspects -----------

%\section{Personal Aspets}
%  \vspace{6pt}
%  \resumeSubHeadingListStart
%    \small{\item{
        
%        \textbf{Father Name :}{ Rengaraj G} \\ \vspace{3pt}
%        \textbf{Total Experience :}{ 2.8 years} \\ \vspace{3pt}
%        \textbf{Current CTC :}{ 4 LPA} \\ \vspace{3pt}
%        \textbf{Expected CTC :}{ As Per Standards } \\ \vspace{3pt}
%        \textbf{Notice Period :}{ 3 Months} \\ \vspace{3pt}
%        \textbf{Marital Status :}{ Single} \\ \vspace{3pt}
%        \textbf{Personal Traits :}{ Interested in learning new things, Smart working, Excellent leadership skills, Willing to Travel and Flexible.} \\ \vspace{3pt}
%        \textbf{Linguistic communication :}{ English, Tamil, Kannada, Telugu} \\ \vspace{3pt}
%    }}
%  \resumeSubHeadingListEnd


%----------- DECLARATION -----------

\section{Declaration}
  \vspace{6pt}
  
  {\textbf{I hereby declare that the details furnished above are true and correct to the best of my knowledge.}}
  
  \begin{flushleft}
    \textbf{Place: Bangalore, Karnataka}
  \end{flushleft}
  
  \begin{flushright}
    \textbf{-- Yogalakshmi Palanivel}
  \end{flushright}


%-------------------------------------------
\end{document}
